A generic and fast C++ optimization framework

### 2017-10-17 paper.tex
Add example comparison table.

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}

@@

\usepackage{nips_2017}

@@

@@

\author{
  Shikhar Bhardwaj \\
  \AND
  Yannis Mentekidis \\
  \AND
  Marcus Edel \\
  \AND
  Ryan R. Curtin \\
  Symantec Corporation \\
}

@@

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{tabularx}
\usepackage{threeparttable}

@@

\usepackage[]{nips_2017}

@@

\newcommand*\rot{\rotatebox{90}}
\newcommand*\OK{\ding{51}}

@@

\author{
  Shikhar Bhardwaj \\
  \AND
  Yannis Mentekidis \\
  \AND
  Marcus Edel \\
  Free University of Berlin \\
  Arnimallee 7, 14195 Berlin \\
  \texttt{marcus.edel@fu-berlin.de} \\
  \AND
  Ryan R. Curtin \\
  Symantec Corporation \\
}

@@

% Just to get a feeling of the look; Also, we could also just use \OK instead of \CURCLE or \LEFTcircle
\begin{table}
\centering
    \begin{tabular}{@{} cl*{4}c @{}}
        & & \multicolumn{4}{c}{} \\[2ex]
        & & \rot{has framework}
          & \rot{\shortstack[l]{problem-independent\\constraints}}
          & \rot{supports x}
          & \rot{supports x} \\
        \cmidrule{2-6}
        & mlpack             & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE  \\
        & vowpal wabbit      &  - & - & -  & -  \\
        & TensorFlow         &  - & -  & -  & -  \\
        & scikit-learn       &  - & -  & -  & - \\
        & scipy              &  - & \LEFTcircle  & \LEFTcircle  & \LEFTcircle \\
        \cmidrule[1pt]{2-6}
    \end{tabular}
    \begin{tablenotes}\footnotesize
\item[*] Library feature comparison: \CIRCLE=\text{provides feature}, \LEFTcircle=\text{partially provides feature}, -=\text{does not provide feature}
\end{tablenotes}
\end{table}
